Artistic Curve Steganography Carried by Musical Audio

### 2022-10-30 writeup/paper.tex
Adding figure on length distortion
Added batch script to create turk samples

@@

In this way, $X$ has $N-\ell+1$ samples.  Let's assume momentarily that $T$ has exactly this many samples; we will address the general case in Section~\ref{sec:reparam}.  We also chose to hide each coordinate in a single frequency bin $k$; we'll index each dimension $i$'s frequency bin as $k_i$.  Then our goal is to find a perturbed version of the magnitudes, $\hat{M}$.  We minimize the following objective function one coordinate dimension $k = 1, ... d$ at a time:

@@

subject to .  This can be formulated as a sparse nonnegative least squares problem.  Though Equation~\ref{eq:objfn} suggest an $O(N \ell)$ time complexity, the linear operator and its adjoint can be implemented with a number of operations proportional to $N$ only, and independent of $\ell$, using the 1D version of the ``summed area tables'' trick in computer vision \cite{lewisfast}; that is, if we let

@@

@@

We ask questions similar to the authors of \cite{cvejic_wavelet_2002}.

>>>>

Pipeline is simple enough that we have very good intuition for how it's working, and we validate its performance in Section~\ref{sec:experiments}.

@@

In this way, $X$ has $N-\ell+1$ samples.  Let's assume momentarily that $T$ has exactly this many samples; we will address the case where $len(T) > N-\ell+1$ in Section~\ref{sec:reparam}.  We also chose to hide each coordinate in a single frequency bin $k$; we'll index each dimension $i$'s frequency bin as $k_i$.  Then our goal is to find a perturbed version of the magnitudes, $\hat{M}$.  We minimize the following objective function one coordinate dimension $k = 1, ... d$ at a time:

@@

subject to .  This can be formulated as a sparse nonnegative least squares problem.  Though Equation~\ref{eq:objfn} suggest an $O(N \ell)$ time complexity to evaluate the objective function, the linear operator and its adjoint can be implemented with a number of operations proportional to $N$ only, and independent of $\ell$, using the 1D version of the ``summed area tables'' trick in computer vision \cite{lewisfast}; that is, if we let

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{OptimalShift.pdf}
  \caption{Curve length can be used as a proxy for distortion.}
  \label{fig:TSPTour}
\end{figure}

@@

We can actually get higher SNRs using frequencies that are more audible

We ask questions similar to the authors of \cite{bassia2001robust}.
